Measurement and Probability in Fuzzy Quantum Theories

### 2017-02-01 prop.tex
prop.tex \section{Properties of Quantum IVPMs Decided by Their Range} Added...

>>>>

\section{Properties of Quantum IVPMs Decided by Their Range}

\begin{lemma}Consider a collection of intervals~$\mathscr{I}$ with
a function~$\iota:\left[0,1\right]\rightarrow\mathscr{I}$ such that
$\iota\left(0\right)=\left[0,0\right]$, $\iota\left(1\right)=\left[1,1\right]$,
$\iota\left(1-x\right)=\left[1,1\right]-\iota\left(x\right)$, and
$\iota\left(\sum{}_{i=1}^{N}x_{i}\right)\subseteq\sum{}_{i=1}^{N}\iota\left(x_{i}\right)$.
Then, given a quantum probability measure~$\mu:\events\rightarrow\left[0,1\right]$,
we define a quantum interval-valued probability measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$
by $\bar{\mu}(P)=\iota\left(\mu(P)\right)$.\end{lemma}
\begin{proof}
~
\begin{itemize}
\item $\bar{\mu}(\mathbb{0})=\iota\left(\mu(\mathbb{0})\right)=\iota\left(0\right)=\left[0,0\right]$.
\item $\bar{\mu}(\mathbb{1})=\iota\left(\mu(\mathbb{1})\right)=\iota\left(1\right)=\left[1,1\right]$. 
\item For any projection $P$, $\bar{\mu}\left(\mathbb{1}-P\right)=\iota\left(\mu(\mathbb{1}-P)\right)=\iota\left(1-\mu(P)\right)=\left[1,1\right]-\iota\left(\mu(P)\right)=\left[1,1\right]-\bar{\mu}\left(P\right)$. 
\item For a set of mutually orthogonal projections $\left\{ P_{i}\right\} _{i=1}^{N}$,
we have $\bar{\mu}\left(\sum_{i=1}^{N}P_{i}\right)=\iota\left(\mu\left(\sum_{i=1}^{N}P_{i}\right)\right)=\iota\left(\sum_{i=1}^{N}\mu\left(P_{i}\right)\right)\subseteq\sum_{i=1}^{N}\iota\left(\mu\left(P_{i}\right)\right)=\sum_{i=1}^{N}\bar{\mu}\left(P_{i}\right)$. 
\end{itemize}
\end{proof}
\begin{lemma}Consider a collection of intervals~$\mathscr{I}$ with
a function~$\iota:\left[0,1\right]\rightarrow\mathscr{I}$ such that
$\iota\left(0\right)=\left[0,0\right]$, $\iota\left(1\right)=\left[1,1\right]$,
$\iota\left(1-x\right)=\left[1,1\right]-\iota\left(x\right)$, and
$\iota\left(\sum{}_{i=1}^{N}x_{i}\right)\subseteq\sum{}_{i=1}^{N}\iota\left(x_{i}\right)$.
Then, there is a quantum interval-valued probability measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$
such that $\mathrm{core}\left(\bar{\mu}\right)$ has an unique element.\end{lemma}
\begin{proof}
Consider $\bar{\mu}(P)=\iota\left(\mu_{\ket{0}}^{B}(P)\right)$. Then,
$\bar{\mu}\left(\proj{0}\right)=\iota\left(\mu_{\ket{0}}^{B}\left(\proj{0}\right)\right)=\iota\left(1\right)=\left[1,1\right]$,
i.e., for any quantum probability measure~$\mu\in\mathrm{core}\left(\bar{\mu}\right)$,
we have $\mu\left(\proj{0}\right)=1$. Therefore, $\mu=\mu_{\ket{0}}^{B}$.
\end{proof}
\footnote{\yutsung{Examples of $\mathscr{I}$ with a function~$\iota:\left[0,1\right]\rightarrow\mathscr{I}$
such that $\iota\left(0\right)=\left[0,0\right]$, $\iota\left(1\right)=\left[1,1\right]$,
$\iota\left(1-x\right)=\left[1,1\right]-\iota\left(x\right)$, and
$\iota\left(\sum{}_{i=1}^{N}x_{i}\right)\subseteq\sum{}_{i=1}^{N}\iota\left(x_{i}\right)$.}}
